Predicting virus-receptor mutant binding by molecular dynamics simulation

### 2013-07-19 paper.tex
Fixed the two formatting mistakes from the JCTC submission.

\author{Austin G. Meyer}
\email{austin.meyer@utexas.edu}
\phone{+1 512 971 0123}
\affiliation{Section of Integrative Biology, Institute for Cellular and Molecular Biology, and Center for Computational Biology and Bioinformatics, The University of Texas at Austin, Austin, TX 78731, USA}
\altaffiliation{Current address: School of Medicine, Texas Tech University Health Sciences Center, Lubbock, TX, 79430, USA}
\altaffiliation{Department of Molecular Biosciences, Institute for Cellular and Molecular Biology, The University of Texas at Austin, Austin, TX 78731, USA}

@@

\begin{acknowledgement}
This work was carried out using high-performance computing resources provided by the High Performance Computing Center (HPCC) at Texas Tech University at Lubbock (http://www.hpcc.ttu.edu) and the Texas Advanced Computing Center (TACC) at The University of Texas at Austin (http://www.tacc.utexas.edu). The authors acknowledge Bryan Sutton for opening access to the Hrothgar cluster.

This work was supported by the Defense Threat Reduction Agency (HDTRA1-12-C-0007) to A.D.E., S.L.S., and C.O.W., the National Science Foundation (MCB-0943383) and the Welch Foundation (F-1654) to A.D.E., the National Institutes of Health (R01-GM088344) to C.O.W., and the National Institutes of Health (R01-GM093086) to S.L.S.
\end{acknowledgement}

>>>>

\author{Austin G. Meyer}
\email{austin.meyer@utexas.edu}
\phone{+1 512 971 0123}
\affiliation{Section of Integrative Biology, Institute for Cellular and Molecular Biology, and Center for Computational Biology and Bioinformatics, The University of Texas at Austin, Austin, TX 78731, USA}
\alsoaffiliation{School of Medicine, Texas Tech University Health Sciences Center, Lubbock, TX, 79430, USA}
\alsoaffiliation{Department of Molecular Biosciences, Institute for Cellular and Molecular Biology, The University of Texas at Austin, Austin, TX 78731, USA}

@@

\section{Acknowledgements}
This work was carried out using high-performance computing resources provided by the High Performance Computing Center (HPCC) at Texas Tech University at Lubbock \\ (http://www.hpcc.ttu.edu) and the Texas Advanced Computing Center (TACC) at The University of Texas at Austin (http://www.tacc.utexas.edu). The authors acknowledge Bryan Sutton for opening access to the Hrothgar cluster.

This work was supported by the Defense Threat Reduction Agency (HDTRA1-12-C-0007) to A.D.E., S.L.S., and C.O.W., the National Science Foundation (MCB-0943383) and the Welch Foundation (F-1654) to A.D.E., the National Institutes of Health (R01-GM088344) to C.O.W., and the National Institutes of Health (R01-GM093086) to S.L.S.
